---
title: "FinalReplication"
author: "cjlw2020"
date: "12/11/2019"
output: html_document
---
#Packages Needed
```{r}
library(lme4)
library(car)
library(optimx)
library(deSolve)
library(ggplot2)
library(data.table)
```
```{r}
 setwd("C:/Users/clint/Desktop/AN597_Project/Individule/doi_10.5061_dryad.0r31r__v1")
df <- read.table("hog.txt", header = TRUE)
head(df)
```

```{r}
summary(df)
```
```{r}
plot(df)
```
#Non-linear least squares attempt:
```{r}
mass <- c(df$mass)
age1 <- c(df$age)
age <- age1/365 #Changes age from days to years
m <-nls(mass~a*age/(b+age))
cor(mass,predict(m)) #Shows how well the model fits
```

```{r}
plot(age,mass)
lines(age,predict(m),lty=2,col="red",lwd=3)
```
#Find Rate of Growth
```{r}
RoG <- (log(max(mass)/min(mass)))/(max(age)) 
RoG #Rate of Growth, didnt work
```
```{r}
a_start<- 0.2 #param a is the y value when "x=0"
b_start<- 0.06523683 #b is the growth rate
```
```{r}
k <-nls(mass~a*exp(-b*age),start=list(a=a_start,b=b_start))
cor(mass,predict(k)) 
```
```{r}
plot(age,mass)
lines(age,predict(k),col="red",lty=2,lwd=3) #This is not working properly
```

#Models

Starting Variables
```{r}
t1 <- max(mass) #maximum value from the data, our starting  value for "theta1", parameter for the asymptote of growth
new <- lm(logit(mass/t1)~age,data=df) #logistic values for mass divided by the asymptote (an approximation of the curve values for each individual)
t2 <- new$coef[1] #starting value for "theta2", parameter of the midpoint of the growth curve
t3 <- new$coef[2] #starting value for "theta3", parameter of the rate of growth
```

#Logistic Model:
```{r}
l <- function(age,theta1,theta2,theta3) {theta1/(1+exp(-(theta2+theta3*age)))} #here we're writing out the function for logistic growth (this is how we tell R what function we're using to model growth... like the function in the table in your paper), which estimates parameters "theta1", "theta2", and "theta3" for changes in a variable (like "BW") based on "AGE".
model.logistic <- nls(mass ~ theta1/(1+exp(-(theta2+theta3*age))), data=df, start=list(theta1=t1,theta2=t2,theta3=t3))
```
or...
```{r}
model.logistic <- nls(mass ~ l(age,theta1,theta2,theta3), data=df, start=list(theta1=t1,theta2=t2,theta3=t3))
summary(model.logistic) #this should give you the estimates for "theta1", "theta2", and "theta3" based on the data.
```
```{r, fig.width= 4,fig.height=4}
t <- ggplot(data = df, aes(age,mass)) +
  geom_smooth(model = model.logistic, se = TRUE, color = "red", size = 0.5, linetype = 2, alpha = 0.15)  +
  geom_point(aes(age,mass), size = 1, shape = 21, stroke = 1) +
  theme_test() +
  scale_y_continuous(lim = c(0.20, 0.56), breaks = c(0.24,0.28, 0.32, 0.36, 0.40, 0.44, 0.48, 0.52, 0.56))
  #scale_x_continuous(lim = c(0, 15), breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15))
t <- t + xlab("Age (years)") + ylab("Lens mass (g)") 
t
```
#Trying to place model properly into graph, not working
```{r, fig.width= 4,fig.height=4}
plot(age,mass)
lines(age,predict(model.logistic),col="red",lty=2,lwd=1)
```
Confidence interval maybe
```{r}
conf <- confint(model.logistic)
conf
```
```{r}
plot(mass ~ age) #this doesnt work, tried to figure out the confidence interval
lines(age, fitted(model.logistic), lty = 2, col = "red", lwd = 2)
lines(age, model.logistic(1:100, conf[1, 1], conf[2, 1], conf[3, 1], conf[4, 1]), lty = 2, 
    lwd = 1, col = "blue")
lines(age, model.logistic(1:100, conf[1, 2], conf[2, 2], conf[3, 2], conf[4, 2]), lty = 2, 
    lwd = 1, col = "blue")
```

#Gompertz Modle: 
For Gompertz, everything the same, but the equation/function used (again, for Lord you'd get this from translating the model equations in your table to R code):
```{r}
g <- function(age,theta1,theta2,theta3){theta1*exp(-exp(-(theta3*(age-theta2))))}
model.gompertz <- nls(mass ~ theta1*exp(-exp(-(theta3*(age-theta2)))), data=df, start=list(theta1=t1,theta2=t2,theta3=t3))
```
or...
```{r}
model.gompertz <- nls(mass ~ g(age,theta1,theta2,theta3), data=df, start=list(theta1=t1,theta2=t2,theta3=t3))
summary(model.gompertz)
```
```{r, fig.width= 4,fig.height=4}
plot(age,mass)
lines(age, predict(model.gompertz),col="red",lty=2,lwd=1)
```
```{r, fig.width= 4,fig.height=4}
p <- ggplot(data = df, aes(age,mass)) +
  geom_smooth(model = model.gompertz, color = "red", size = 0.5, linetype = 2, alpha = 0.15)  +
  geom_point(aes(age,mass), size = 1, shape = 21, stroke = 1) +
  theme_test() +
  scale_y_continuous(lim = c(0.20, 0.56), breaks = c(0.24,0.28, 0.32, 0.36, 0.40, 0.44, 0.48, 0.52, 0.56))
  #scale_x_continuous(lim = c(0, 15), breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15))
p <- p + xlab("Age (years)") + ylab("Lens mass (g)") 
p
```

#Lord Model: Something isn't right because every figure looks the same
```{r}
#Lord Model 
L <- function(age,theta1,theta3,alpha){theta1*exp(-theta3/age + 0.62)}
lord.model <- nls(mass ~ L(age,theta1,theta3), data=df, start=list(theta1=t1,theta3=t3))
summary(lord.model)
```
```{r, fig.width= 4,fig.height=4}
plot(age,mass)
lines(age,predict(lord.model),col="red",lty=2,lwd=1)
```
```{r, fig.width= 4,fig.height=4}
p <- ggplot(data = df, aes(age,mass)) +
  geom_smooth(model = lord.model, color = "red", size = 0.5, linetype = 2, alpha = 0.15)  +
  geom_point(aes(age,mass), size = 1, shape = 21, stroke = 1) +
  theme_test() +
  scale_y_continuous(lim = c(0.20, 0.56), breaks = c(0.24,0.28, 0.32, 0.36, 0.40, 0.44, 0.48, 0.52, 0.56))
  #scale_x_continuous(lim = c(0, 15), breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15))
p <- p + xlab("Age (years)") + ylab("Lens mass (g)") 
p
```

#Tables

#Table 1.
```{r}
head(age)
```

```{r}
Age_class_years <- c(0:10,"Total")
n <- c(23,20,12,10,19,9,5,3,3,2,5,11)
T1.df <- data.frame(Age_class_years,n)
T1.df
```
```{r}
setDT(T1.df)
```

#Table
